Summary Tables

### 2020-02-21 summary_tables_outcomes.Rmd
Add DT for whw for all cities where users can select columns of interest

for (cs in names(all_whw)){

@@

@@

@@

>>>>

st <- list()

td <- NULL

for (cs in names(all_whw)){
  # cs <- 'Baseline'

@@

   unk <- td %>% filter(mode %in% c('unknown', 'unk')) %>% summarise_if(is.numeric, funs(sum)) %>% mutate(mode = 'unknown')

   unsp <- td %>% filter(mode %in% c('unspecified', 'listed_na', '?')) %>% summarise_if(is.numeric, funs(sum)) %>% mutate(mode = 'unspecified')

   other <- unsp <- td %>% filter(mode %in% c('other', 'non.motor.vehicle', 'tract', 'railway.train.railway.vehicle')) %>% summarise_if(is.numeric, funs(sum)) %>% mutate(mode = 'other')

   pu <- td %>% filter(mode %in% c('picku', 'pickup/light goods')) %>% summarise_if(is.numeric, funs(sum)) %>% mutate(mode = 'pickup')

   bus <- td %>% filter(mode %in% c('bus', 'bus_driver')) %>% summarise_if(is.numeric, funs(sum)) %>% mutate(mode = 'bus')

   td <- td %>% filter(!mode %in% c('bus', 'bus_driver', 'unknown', 'unk', 'unspecified', 'listed_na', '?', 
                                  'other', 'non.motor.vehicle', 'tract', 'railway.train.railway.vehicle',
                                  'picku', 'pickup/light goods'))

   td <- plyr::rbind.fill(td, bus, unk, unsp, other, pu)

   td <- (td[!duplicated(td), ])

@@

   td <- td %>% mutate_if(is.numeric, round, 2)

   readr::write_csv(td, paste0('results/multi_city/whw_', cs, '.csv'))

   st[[cs]] <- format(td, scientific = F)

@@

### DT - Who hit whom matrix for all case cities {#whw_all}

#### Baseline

```{r dt}

#for (cs in names(all_whw)){
td <- NULL

cs <- 'Baseline'

fname <- paste("whw", cs)

td <- st[[cs]]

DT::datatable(td, 
              extensions = 'Buttons',
              escape = FALSE,
              rownames = FALSE,
              options = list(dom = 'Bfrtip',
                             buttons = 
                               list('colvis', list(
                                 extend = 'collection',
                                 buttons = list(list(extend='csv',
                                                     filename = fname),
                                                list(extend='excel',
                                                     filename = fname)),
                                 text = 'Download'
                               )),
                             scrollX = TRUE,
                             pageLength = nrow(td),
                             order=list(list(2,'desc')),
                             columnDefs = list(list(visible=FALSE, targets=c(1:(ncol(td) - 1))))))

# }
